### 2014-10-12 writing/AAAI SSS '15/join.tex
Post-merge cleanup.

\paragraph{Experiments}
To test our models' ability to learn these inferential patterns, we
create artificial boolean structures in which terms denote sets of entities from
a small domain (e.g., Figure~\ref{lattice-figure}), employ logical
deduction to identify the valid statements, divide those into train
and test sets, and remove from the test set those statements which
cannot be proven from the training statements
(Figure~\ref{unprovable}).
% using the logic depicted in Figure~\ref{lattice-figure}.
%
%
% We test the model's ability to learn this behavior by creating
% artificial data sets of terms which represent sets of numbers. Since
% MacCartney and Manning's set of relations hold between sets as well as
% between sentences, we can use the underlying set structure to generate
% the all of the relations that hold between any pair of these terms, as
% in Figure \ref{lattice-figure}. We train the model defined above on a
% subset of these relations, but rather then presenting the model with a
% pair of tree-structured sentences as inputs, simply present it with
% two single terms, each of which corresponds to a single vector in the
% (randomly initialized) vocabulary matrix $V$, ensuring that the model
% has no information about the terms being compared except the relations
% between them.
%
In our experiments, we create 80 randomly generated sets drawn from a
domain of seven elements. This yields 6400 statements about pairs of
formulae, of which 3200 are chosen as a test set, and that test set is
further reduced to the 2960 examples that can be provably derived from
the training data. We trained both the NN model and the NTN model on
these data
sets% . In both cases, the models were implemented exactly as
% described in Section~\ref{methods}, but since the items being compared
% are single terms rather than full tree structures, the composition
% layer was not involved, and the two models differed only in which
% layer function was used for the comparison layer. We simply present
% the models with two single terms, each of which corresponds to a
% single vector in the (randomly initialized) vocabulary matrix $V$,
% thereby ensuring that the model has no information about the terms
% being compared except the relations between them.

\paragraph{Results} 
We found that the NTN model worked best with 11-dimensional vector
representations for the 80 sets and a 90-dimensional feature vector
for the classifier, though the performance of the model was not highly
dependant on either dimensionality setting. 
Averaging over five randomly generated datasets, the model was able to correctly label 98.1\% (standard error $0.67\%$) of the provably derivable test examples, and 87.7\%
($SE = 3.59\%$) of the remaining test examples. The simpler NN worked
best with 11 and 75 dimensions, respectively, but was able to achieve
accuracies of only 84.8\% ($SE = 0.84\%$) and 68.7\% ($SE = 1.58\%$),
respectively. Training accuracy was 99.8\% ($SE = 0.04\%$) for the NTN and 94.7\% ($SE= 0.89\%$) for
the NN.

>>>>

\paragraph{Experiments}
To test our models' ability to learn these inferential patterns, we
create artificial boolean structures in which terms denote sets of entities from
a small domain (e.g., Figure~\ref{lattice-figure}), employ logical
deduction to identify the valid statements, divide those into train
and test sets, and remove from the test set those statements which
cannot be proven from the training statements
(Figure~\ref{unprovable}).
% using the logic depicted in Figure~\ref{lattice-figure}.
%
%
% We test the model's ability to learn this behavior by creating
% artificial data sets of terms which represent sets of numbers. Since
% MacCartney and Manning's set of relations hold between sets as well as
% between sentences, we can use the underlying set structure to generate
% the all of the relations that hold between any pair of these terms, as
% in Figure \ref{lattice-figure}. We train the model defined above on a
% subset of these relations, but rather then presenting the model with a
% pair of tree-structured sentences as inputs, simply present it with
% two single terms, each of which corresponds to a single vector in the
% (randomly initialized) vocabulary matrix $V$, ensuring that the model
% has no information about the terms being compared except the relations
% between them.
%
In our experiments, we create 80 randomly generated sets drawn from a
domain of seven elements. This yields 6400 statements about pairs of
formulae, of which 3200 are chosen as a test set, and that test set is
further reduced to the 2960 examples that can be provably derived from
the training data. We trained both the NN model and the NTN model on
these data
sets.% . In both cases, the models were implemented exactly as
% described in Section~\ref{methods}, but since the items being compared
% are single terms rather than full tree structures, the composition
% layer was not involved, and the two models differed only in which
% layer function was used for the comparison layer. We simply present
% the models with two single terms, each of which corresponds to a
% single vector in the (randomly initialized) vocabulary matrix $V$,
% thereby ensuring that the model has no information about the terms
% being compared except the relations between them.

\paragraph{Results} 
We found that the NTN model worked best with 11-dimensional vector
representations for the 80 sets and a 90-dimensional feature vector
for the classifier, though the performance of the model was not highly
dependant on either dimensionality setting. 
Averaging over five randomly generated data sets, the model was able to correctly label 98.1\% (standard error $0.67\%$) of the provably derivable test examples, and 87.7\%
($SE = 3.59\%$) of the remaining test examples. The simpler NN worked
best with 11 and 75 dimensions, respectively, but was able to achieve
accuracies of only 84.8\% ($SE = 0.84\%$) and 68.7\% ($SE = 1.58\%$),
respectively. Training accuracy was 99.8\% ($SE = 0.04\%$) for the NTN and 94.7\% ($SE= 0.89\%$) for
the NN.

### 2014-10-12 writing/AAAI SSS '15/wordnet.tex
Tweaks to stats reporting.
Post-merge cleanup.

\begin{table}[h]
\centering\resizebox{5.5in}{!}{
  \setlength{\tabcolsep}{15pt}
  \renewcommand{\arraystretch}{1.1}
  \begin{tabular}{r r@{ }r r@{ }r r@{ }r r@{ }r r@{ }r} 
    \toprule
     Portion of & \multicolumn{4}{c}{NN} & \multicolumn{4}{c}{NTN} & \multicolumn{2}{c}{Baseline}\\
     training data  & \multicolumn{2}{c}{w/ GloVe} & \multicolumn{2}{c}{w/o GloVe} & \multicolumn{2}{c}{w/ GloVe} & \multicolumn{2}{c}{w/o GloVe} \\
    \midrule
     100\%   & 99.7 &(0.0) & 99.4$^\dagger$ &(0.3)    & 99.6 &(0.0) & \textbf{100.0}\nodagger &(0.1) & 37.9 &(--)\\
     33\%    & 96.0 &(0.5) & 95.3\nodagger &(0.2)     & 95.8 &(0.8)          & 95.5$^\dagger$ &(0.5) & 37.9 &(--)\\
     11\%    & 91.1 &(0.5) & 90.8$^\dagger$ &(0.3)    & 91.3 &(0.6)          & 90.9$^\dagger$ &(0.2) & 37.9 &(--)\\
     % 2\%    & 86.0 &(100.0) & ... &(100.0)   & 86.2 &(100.0)           & 76.4 &(87.3) & 37.9 &(--)\\ % Accidental run with slightly different train/test split.
    \bottomrule
  \end{tabular}}
 \caption{Mean test \% accuracy scores (with standard deviations) on the WordNet data over five-fold crossvalidation. The baseline figure is the frequency of the most frequent class, \ii{coordinate}.\label{wordnet-table}} 
\end{table}

>>>>

\begin{table}[h]
\centering\resizebox{5.5in}{!}{
  \setlength{\tabcolsep}{15pt}
  \renewcommand{\arraystretch}{1.1}
  \begin{tabular}{r r@{ }r r@{ }r r@{ }r r@{ }r r@{ }r} 
    \toprule
     Portion of & \multicolumn{4}{c}{NN} & \multicolumn{4}{c}{NTN} & \multicolumn{2}{c}{Baseline}\\
     training data  & \multicolumn{2}{c}{w/ GloVe} & \multicolumn{2}{c}{w/o GloVe} & \multicolumn{2}{c}{w/ GloVe} & \multicolumn{2}{c}{w/o GloVe} \\
    \midrule
     100\%   & 99.73 &(0.04) & 99.37$^\dagger$ &(0.14)    & 99.61 &(0.02) & \textbf{99.95}\nodagger &(0.03) & 37.05 &(--)\\
     33\%    & 95.96 &(0.20) & 95.30\nodagger &(0.12)                & 95.83 &(0.35)          & 95.45$^\dagger$ &(0.31) & 37.05 &(--)\\
     11\%    & 91.11 &(0.24) & 90.81$^\dagger$ &(0.20)    & 91.27 &(0.27)          & 90.90$^\dagger$ &(0.13) & 37.05 &(--)\\
     % 2\%    & 86.0 &(100.0) & ... &(100.0)   & 86.2 &(100.0)           & 76.4 &(87.3) & 37.9 &(--)\\ % Accidental run with slightly different train/test split.
    \bottomrule
  \end{tabular}}
 \caption{Mean test \% accuracy scores (with standard error) on the WordNet data over five-fold crossvalidation. The baseline figure is the frequency of the most frequent class, \ii{hypernym}.\label{b-table}} 
\end{table}
